Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2024-02-12 manuscript/main.tex
update affiliations

	\author[Heumos, Guarracino \textit{et~al}.]{
        Simon~Heumos\,$^{\orcidlink{0000-0003-3326-817X}1,2,\dagger}$,
        Andrea~Guarracino\,$^{\orcidlink{0000-0001-9744-131X}3,4,\dagger}$,
        Jan-Niklas M. Schmelzle\,$^{\orcidlink{0000-0001-8566-4049}5,6}$,
        Jiajie Li\,$^{\orcidlink{0000-0002-6775-2843}6}$,
        Zhiru Zhang\,$^{\orcidlink{0000-0002-0778-0308}6}$,
        Jörg Hagmann\,${\orcidlink{0000-0002-7232-3103}^7}$,
        Sven Nahnsen\,$^{\orcidlink{0000-0002-4375-0691}1,2,8}$,
        Pjotr Prins\,$^{\orcidlink{0000-0002-8021-9162}3}$,
        Erik~Garrison\,$^{\orcidlink{0000-0003-3821-631X}\text{\sfb 3},*}$
    }

    \address{
        $^1$Quantitative Biology Center (QBiC), University of Tübingen, Tübingen 72076, Germany \\
        $^2$Biomedical Data Science, Department of Computer Science, University of Tübingen, Tübingen 72076, Germany \\
        $^3$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, TN 38163, USA \\
        $^4$Genomics Research Centre, Human Technopole, Milan 20157, Italy \\
        $^5$Department of Computer Engineering, School of Computation, Information and Technology (CIT), Technical University of Munich, Munich 80333, Germany \\
        $^6$School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14853, USA \\
        $^7$Computomics GmbH, Eisenbahnstr. 1, 72072 Tübingen, Germany \\
        $^8$M3 Research Center, University Hospital Tübingen, 72076 Tübingen, Germany \\
    }

>>>>

	\author[Heumos, Guarracino \textit{et~al}.]{
        Simon~Heumos\,$^{\orcidlink{0000-0003-3326-817X}1,2,3,4\dagger}$,
        Andrea~Guarracino\,$^{\orcidlink{0000-0001-9744-131X}5,6,\dagger}$,
        Jan-Niklas M. Schmelzle\,$^{\orcidlink{0000-0001-8566-4049}7,8}$,
        Jiajie Li\,$^{\orcidlink{0000-0002-6775-2843}8}$,
        Zhiru Zhang\,$^{\orcidlink{0000-0002-0778-0308}8}$,
        Jörg Hagmann\,${\orcidlink{0000-0002-7232-3103}^9}$,
        Sven Nahnsen\,$^{\orcidlink{0000-0002-4375-0691}1,2,3,4}$,
        Pjotr Prins\,$^{\orcidlink{0000-0002-8021-9162}5}$,
        Erik~Garrison\,$^{\orcidlink{0000-0003-3821-631X}\text{\sfb 5},*}$
    }

    \address{
        $^1$Quantitative Biology Center (QBiC), University of Tübingen, Tübingen 72076, Germany \\
        $^2$Biomedical Data Science, Department of Computer Science, University of Tübingen, Tübingen 72076, Germany \\
        $^3$M3 Research Center, University Hospital Tübingen, Tübingen 72076 , Germany \\
        $^4$Institute for Bioinformatics and Medical Informatics (IBMI), University of Tübingen, Tübingen 72076, Germany \\
        $^5$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, TN 38163, USA \\
        $^6$Genomics Research Centre, Human Technopole, Milan 20157, Italy \\
        $^7$Department of Computer Engineering, School of Computation, Information and Technology (CIT), Technical University of Munich, Munich 80333, Germany \\
        $^8$School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14853, USA \\
        $^9$Computomics GmbH, Eisenbahnstr. 1, 72072 Tübingen, Germany \\
    }
